Methods to prioritise pop-up active transport infrastructure

### 2020-05-09 article.Rmd
Update geographic subsetting figure

<!-- due to cuts in services and fear of being infected while in enclosed spaces, meaning that walking and particularly cycling may be the only way that workers can reach key destinations such as hospitals. -->

<!-- From a physical activity perspective this change is welcome: obesity is a powerful predictor of all-cause mortality, including from Covid-19 [@docherty_features_2020]. -->
<!-- From a physical distancing perspective, increased levels of walking and cycling, -->
<!-- the shift creates pressure on governments to ensure sufficient 'space for social distancing', while enabling increased active mobility for health and travel to key workplaces. -->
<!-- particularly in densly populated urban areas where pavements and cycleways may be narrow,  -->

Local and national governments are working out how best to respond.
Many options are available to ensure that citizens can benefit from outdoor activity while minimizing health risks, ranging from the hand sanitiser provision to the creation of extra active transport space [@freeman_covid19_2020].
Installation of 'pop-up' active transport infrastructure has been endorsed and implemented in many places [@laker_world_2020].
The Scottish government, for example, has provided £10m "to keep key workers moving" by "reallocating road space to better enable this shift and make it safer for people who choose to walk, cycle or wheel for essential trips or for exercise" [@transportscotland_10_2020].
Most pop-up active transport infrastructure can be classified into three broad categories:

@@

```{r parameters}
min_cycling_potential = 0
min_grouped_cycling_potential = 100
min_grouped_length = 500
city_centre_buffer_radius = 8000
city_centre = tmaptools::geocode_OSM("leeds", as.sf = TRUE)
city_centre_buffer = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius)
h_leeds = hsf[city_centre_buffer, ]
```

@@

```{r gsub, fig.cap="Illustration of geographic subsetting based on distance to the city centre rather than based on location within somewhat arbitrarily shaped city boundaries"}
# nrow(r_central)
# nrow(rj)
square = stplanr::geo_bb(shp = city_centre_buffer)
m1 = tm_shape(r_main_region) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(region) + tm_borders() +
  tm_shape(square) + tm_borders(lty = 3) +
  tm_scale_bar() 
# m1
m2 = tm_shape(r_main) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(city_centre_buffer) + tm_borders() +
  tm_scale_bar() +
  tm_layout(legend.show = FALSE)
tmap_arrange(m1, m2, nrow = 1)
```

## Levels of analysis and grouping

>>>>

<!-- due to cuts in services and fear of being infected while in enclosed spaces, meaning that walking and particularly cycling may be the only way that workers can reach key destinations such as hospitals. -->
<!-- From a physical activity perspective this change is welcome: obesity is a powerful predictor of all-cause mortality, including from Covid-19 [@docherty_features_2020]. -->
<!-- From a physical distancing perspective, increased levels of walking and cycling, -->
<!-- the shift creates pressure on governments to ensure sufficient 'space for social distancing', while enabling increased active mobility for health and travel to key workplaces. -->
<!-- particularly in densly populated urban areas where pavements and cycleways may be narrow,  -->

Local and national governments are working out how best to respond.
Many options are available to ensure that citizens can benefit from outdoor activity while minimizing health risks, ranging from the hand sanitiser provision to the creation of extra active transport space [@freeman_covid19_2020].
Installation of 'pop-up' active transport infrastructure has been endorsed and implemented in many places [@laker_world_2020].
The Scottish government, for example, has provided £10 million "to keep key workers moving" by "reallocating road space to better enable this shift and make it safer for people who choose to walk, cycle or wheel for essential trips or for exercise" [@transportscotland_10_2020].
On 9^th^ May 2020, the UK government announced a £250 million package for pop-up active transport infrastructure [@reid_government_2020].
Evidence is needed to ensure that such investment is spent effectively and were it is most needed.

Most pop-up active transport infrastructure can be classified into three broad categories:

@@

```{r parameters}
min_cycling_potential = 0
min_grouped_cycling_potential = 100
min_grouped_length = 500
city_centre_buffer_radius_small = 5000
city_centre_buffer_radius = 8000
city_centre_buffer_radius_large = 10000
city_centre = tmaptools::geocode_OSM("leeds", as.sf = TRUE)
city_centre_buffer_small = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_small)
city_centre_buffer = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius)
city_centre_buffer_large = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_large)
h_leeds = hsf[city_centre_buffer, ]
```

@@

```{r gsub, fig.cap="Illustration of geographic subsetting based on distance to a central point (Leeds city city centre in this case) rather than based on location within somewhat arbitrarily shaped city boundaries. Radii of 5 km, 8 km and 10 km are shown for reference (note that some roads within 10 km of the center are outside the regional boundary)."}
# nrow(r_central)
# nrow(rj)
square = stplanr::geo_bb(shp = city_centre_buffer)
m1 = tm_shape(r_main_region) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(region) + tm_borders() +
  tm_shape(square) + tm_borders(lty = 3) +
  tm_scale_bar() 
# m1
m2 = tm_shape(r_main) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(city_centre_buffer) + tm_borders() +
  tm_shape(city_centre_buffer_small) + tm_borders() +
  tm_shape(city_centre_buffer_large) + tm_borders() +
  tm_scale_bar() +
  tm_layout(legend.show = FALSE)
tmap_arrange(m1, m2, nrow = 1)
```

## Attribute filtering and grouping
